---
title: "legor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{legor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(legor)
```

## Introduction
__legor__ is an R package that provides lego data spanning the years 2005-2022. The package performs (describe modelling) modelling and creates plots of (describe plotting) variables relationships.

* `fit_lego()`: for fitting a linear regression model to the chosen data.

* `lego_plot()`: for plotting ggplot2 based visualisations.

The purpose of this vignette is to show the intended usage of the 'legor' package. The package contains a data set `lego_data` intended to be used with these functions.

### Installation
First ensure [R](https://cran.r-project.org/) is installed, installing [RStudio](https://www.rstudio.com/) afterwards is optional but recommended to improve user experience. __legor__ runs on Windows, Mac OS X, and Linux. 

In R type the following commands into the Console tab.
```{r, eval = FALSE}
install.packages('devtools')
devtools::install_github('airmid-ms/legor') 
library(legor)
```

Now the __legor__ functions outlined at the beginning of this page, including the dataset, will be accessible.

Visit the [GitHub page](https://github.com/airmid-ms/legor) to install any future package updates. This page can also be used to report any bugs or issues with the package.

Before attempting to use the functions in this package you'll first need to load the relevant data named `lego_data`. __tbr__ The example below demonstrates how to preview the dataset.

```{r}
data(lego_data)
head(lego_data) # to be removed
```
__edit this part out once issue with loading is solved__ First the data will be lazily loaded into your environment as a "promise" type object. It will not be fully loaded into your environment until you call the dataset in another function such as `head()` or `fit_lego()`. To learn more about this data set type
```{r, eval = FALSE}
?lego_data
```



## fit_lego()
This fit method takes objects located in the `lego_data` dataset and incorporates select variables into a linear regression model. ... add info on other models included and their mathematical formulas using LaTEX

* examples


## plot_lego()
need several examples with legends.

can the functions above be nested? if so include example in this section.
